Predictive Modeling of I/O Characteristics \\ in High Performance Computing Systems

### 2017-11-29 HPC_Paper/paper.tex
Finished the HPC paper, ready for review by Dr.Watson. Updated all the figures to have uniform font sizes that should remain legible in print.

\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm}
\usepackage{algorithm}     % needed for the algorithm block
\usepackage{algpseudocode} % algorithmicx psuedo-code styling
%\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}
%% \usepackage[dvips,colorlinks=true,urlcolor=blue,citecolor=black,%
%% anchorcolor=black,linkcolor=black]{hyperref}

@@

where $s$ is the iteration number, $B_l(x)$ and $B_k(x)$ are basis
functions from the previous iteration, $c, v \in \mathbb{R}$, $w_+ =
\{w, w \geq 0, 0, w < 0\},$ and $w_+ = (-w)_+$. After iteratively
constructing a model, MARS then iteratively removes basis functions
that do not contribute to goodness of fit. In effect, MARS creates a
locally component-wise tensor product approximation of the data. The
overall computational complexity of Fast MARS is $\mathcal{O}(n d
m^3)$ where $m$ is the maximum number of underlying basis
functions. This paper uses an implementation of MARS
\shortcite{rudy2017pyearth} with $m = 200$.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,trim={0 .5in 0 1in}]{Raw_Throughput.pdf}
  \caption{Histograms of 100-bin reductions of the PMF of I/O
    throughput mean (top) and I/O throughput sample variance
    (bottom). In the mean plot, the first 1\% bin (truncated in plot)
    has a probability mass of .45. In the variance plot, the first 1\%
    bin has a probability mass of .58. It can be seen that the
    distributions of throughputs are primarily of lower magnitude with
    occasional extreme outliers.}
  \label{fig:raw_throughput}
\end{figure}

\subsection{Dimensional Analysis}
This work utilizes an extension to standard $k$-fold cross validation
that allows for a more thorough investigation of the expected model
performance in a variety of real-world situations. Alongside
randomized splits, two extra components are considered: the amount of
training data provided, and the dimension of the input data. It is
important to consider that algorithms that perform well with less
training input also require less experimentation, although the amount
of training data required may change as a function of the number of
input dimensions, and this needs to be studied as well. The framework
used here will be referred to as a multidimensional analysis (MDA) of
the IOzone data.

\subsubsection{Multidimensional Analysis}
This procedure combines random selection of training and testing
splits with changes in the input dimension and the ratio of training
size to testing size. Given an input data matrix with $n$ rows
(points) and $d$ columns (features), the multidimensional analysis
(MDA) is performed as follows:
\begin{enumerate}
\item for all $k = 1, \ldots, d$ and for all subsets of input features
  $F = \{ j_1, j_2, \ldots j_k \}$; reduce the input data to unique
  points $z \in \mathbb{R}^k$ with $f(z) = E[ \{ f(x^{(i)}) \quad
    \forall i \quad s.t. \quad (x^{(i)}_F = z) \} ]$.
\item for all $r$ in $\{5, 10, \ldots, 95\}$; generate $N$ random
  splits $(train, test)$ of the reduced data with $r$ percentage for
  training and $100 - r$ percentage for testing.
\item when generate each random $(train, test)$ split, ensure that all
  points from $test$ are on or inside the convex hull of points in
  $train$; also ensure that the points in $train$ are well spaced.
\end{enumerate}

In order to ensure that the testing points are inside the convex hull
of training points, this paper identifies the set of (reduced
dimension) points that compose the convex hull and forcibly places
those points in the training set. In order to ensure that training
points are well spaced, this paper relies on the statistical method
for picking points from \shortciteN{amos2014algorithm} that procedes
as follows:
\begin{enumerate}
\item Generate a sequence of all pairs of points sorted by ascending
  pairwise $L_2$ distance between points, ${(x^{(i_1)},x^{(j_1)}),
    (x^{(i_2)},x^{(j_2)}), \ldots}$ such that
  $||x^{(i_k)}-x^{(j_k)}||_2 \leq ||x^{(i_{k+1})}-x^{(j_{k+1})}||_2$
\item Iteratively remove points from candidacy until only $N$ remain
  by sequentially selecting one point from the pair $(x^{(i_k)},
  x^{(j_k)})$ for $k = 1,\ldots$ if both $x^{(i_k)}$ and $x^{(j_k)}$
  are still candidates.
\end{enumerate}

Given the large number of constraints, level of reduction, and use of
randomness in the MDA procedure, occasionally $N$ unique training
testing splits may not be created or may not exist. In these cases, if
there are fewer than $N$ possible splits, those deterministically
generated splits are used. Otherwise after $3*N$ attempts, only the
unique splits are kept for analysis. The MDA procedure has been
implemented in python3 while most regression and interpolation methods
are FORTRAN wrapped with python. All randomness has been seeded for
reproducability.

For any input feature subset $F$ (of size $k$) and selected value of
$r$, MDA will generate up to $N$ predictions that each multivariate
model has made for each point $z^{(i)} \in \mathbb{R}^k$. There may be
fewer than $N$ predictions made for any given point. Points in the
convex hull for the selected subest of features will always be used
for training, never for testing. Points that do not have any close
neighbors will often be used for training in order to ensure well
spacedness. Finally, as mentioned before, some subsets of features do
not readily generate $N$ unique training and testing splits.

MDA results in a distribution of possible estimates that a given
multivariate model could make for a point in $\mathbb{R}^k$, $k \leq
d$ given feature set $F$. The summary results presented in this work
use the expected value of the distributions at each point as the model
estimate for error analysis.

@@

A naive multivariate prediction technique such as nearest neighbor
could experience relative errors in the range $[0,10^m]$ where $m$ is
$log_{10}(\text{max}_f - \text{min}_f)$ when modeling a function $f$
from data. The IOzone mean data response values span 3 orders of
magnitude (as can be seen in Table \ref{tab:data_type}) while variance
data response values span 6 orders of magnitude. It is expected
therefore, that all studied multivariate models perform better than a
naive approach, achieving relative errors strictly less than $10^3$
for mean throughput and $10^6$ when for throughput sample
variance. Ideally, models will yield relative errors significantly
smaller than 1.

@@

Almost all multivariate models analyzed make predictions with a
relative error less than 1 for most system configurations when
predicting the mean I/O throughput of a system given varying amounts
of training data. The overall best of the multivariate models,
Delaunay, consistently makes predictions with relative error less than
$.05$ (5\% error). In figure \ref{fig:mean_tt_ratio} it can also be
seen that the Delaunay model consistently makes good predictions even
with as low as 5\% training data (43 system configurations) regardless
of the dimension of the data.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,trim={0 1in 0 1in}]{Mean_TT_Ratio.pdf}
  \caption{These box plots show the prediction error of means with
    increasing amounts of training data provided to the models. Notice
    that the response values being predicted span 3 orders of
    magnitude and hence relative error in that range would not be
    unexpected. For SVR the top box whisker goes from around 100 to 50
    from left to right and is chopped in order to maintain focus on
    the more performant models.}
  \label{fig:mean_tt_ratio}
\end{figure}

@@

The prediction results for variance resemble that of predicting I/O
throughput mean, with each of the errors being scaled proportional to
the change in scale of the response values. Delaunay remains the best
overall predictor with LSHEP closely competing, but yielding much more
outliers.

\subsection{Increasing Dimension}

As can be seen in figure \ref{fig:mean_dim}, all of the models suffer
increasing error rates in higher dimension. This is expected, because
the number of possible interactions to model grows
exponentially. However, LSHEP and Delaunay maintain the slowest
increase in relative error. The particularly slow increase in error
seen for Delaunay appears to suggest that it is capable of making
predictions with a range of relative errors approximately spanning
\rpm $.2*\text{\textit{dim}}$.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,trim={0 1in 0 2in}]{Mean_Dim.pdf}
  \caption{These box plots show the prediction error of means with
    increasing dimension. }
  \label{fig:mean_dim}
\end{figure}

@@

\subsection{Modeling the System}
\begin{enumerate}
\item Promise of the models, especially Delaunay
\item Possible reasons for the performance differences between models
\item The need for as few as 50 experiments to get less than 5\% error
\item The unfortunate inability of Delaunay to scale to higher dimension
\end{enumerate}

\subsection{Extending the Analysis}
\begin{enumerate}
\item Measuring different system characteristics other than I/O
\item Recording system performance constantly to maintain model accuracy
\end{enumerate}

\section{Conclusion}
\label{sec:conclusion}
\begin{enumerate}
\item Delaunay is the best model, capable of predicting the
  performance of 800 different system configurations accurately after
  only being trained on a well-spaced set of 50 configurations.
\item More comparisons of models similar to Delaunay should be done to
  evaluate what mathematical characteristics of multivariate models are
  most effective.
\end{enumerate}

%     Future Work     
%=====================
\subsection{Future Work}
The most severe limitation to the presented work is the present
inability to model the relationship between categorical system
parameters. This could be seen as a limitation of the models selected,
because only MARS is capable of handling non-numeric variables, or as
a limitation of the MDA framework. Future works could attempt to
identify the viability of reducing categorical variables to numerical
ones to expand set of predictable system configurations.

\begin{enumerate}
\item Using models to predict more complex responses, such as functions
\end{enumerate}

%% \newpage
%% \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\\

@@

%% \texttt{\textbf{L}oc\textbf{A}ll\textbf{Y} li\textbf{NE}ar
%%   \textbf{W}eighted \textbf{A}pproxima\textbf{T}ion\textbf{S}
%%   \textbf{O}f fu\textbf{N}tions}
%% %% L  A  Y   NE   W        A        T   S O    N
%% \newpage

@@

%%  ALGORITHM     MEAN ABSOLUTE ERROR    MEAN RELATIVE ERROR

%% 1 Dimension                                        
%%  Delaunay         2060267             0.03 
%%  MARS             2176368             0.03 
%%  MLPRegressor     2461097             0.06 
%%  LSHEP            6353148             0.06 
%%  SVR             19306731             0.96

%% 2 Dimensions                                       
%%  Delaunay         2916224             0.07 
%%  MARS             6213369             0.61 
%%  MLPRegressor     8883580             0.81 
%%  LSHEP           13038882             1.52 
%%  SVR             78213963             18.49

%% 3 Dimensions                                       
%%  Delaunay         3001794             0.09 
%%  MARS             4024964             0.65 
%%  LSHEP            5446207             1.13 
%%  MLPRegressor    11190977             2.03 
%%  SVR             97761266             31.27

%% 4 Dimensions                                       
%%  Delaunay         3134779             0.10 
%%  MARS             4497414             1.01 
%%  LSHEP            5133648             1.07 
%%  MLPRegressor    11831721             2.20 
%%  SVR            113551300             37.26

%% [5 - 21%] Training Data               
%%  Delaunay         5274933             0.11 
%%  MARS             6543153             0.61 
%%  LSHEP           13218469             2.53 
%%  MLPRegressor    17348982             2.58 
%%  SVR            170906944             49.45

%% [25 - 46%] Training Data              
%%  Delaunay         2898330             0.08 
%%  MARS             4324916             0.80 
%%  LSHEP            4936381             0.85 
%%  MLPRegressor    12504957             2.29 
%%  SVR             99851846             31.28

%% [50 - 74%] Training Data              
%%  Delaunay         1518477             0.07 
%%  LSHEP            2251409             0.26 
%%  MARS             3115943             0.95 
%%  MLPRegressor     5292177             1.17 
%%  SVR             51565405             19.63

%% [75 - 96%] Training Data              
%%  Delaunay          886346             0.08 
%%  LSHEP            1415034             0.15 
%%  MARS             2591451             0.74 
%%  MLPRegressor     2996253             1.02 
%%  SVR             27125130             12.64

%% ALGORITHM   AVG ABSOLUTE MEAN ERROR   AVG RELATIVE ERROR
%% Delaunay         2711394              0.08  
%% MARS             4185947              0.72  
%% LSHEP            6474147              0.94  
%% MLPRegressor     9063718              1.48  
%% SVR             82285323              25.12

>>>>

\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm}
%% \usepackage{color}   % Needed to color text for drafts

%% \usepackage{algorithm}     % needed for the algorithm block
%% \usepackage{algpseudocode} % algorithmicx psuedo-code styling
%\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}
%% \usepackage[dvips,colorlinks=true,urlcolor=blue,citecolor=black,%
%% anchorcolor=black,linkcolor=black]{hyperref}

@@

where $s$ is the iteration number, $B_l(x)$ and $B_k(x)$ are basis
functions from the previous iteration, $c, v \in \mathbb{R}$, $w_+ =
\{w, w \geq 0;\quad 0, w < 0\},$ and $w_+ = (-w)_+$. After iteratively
constructing a model, MARS then iteratively removes basis functions
that do not contribute to goodness of fit. In effect, MARS creates a
locally component-wise tensor product approximation of the data. The
overall computational complexity of Fast MARS is $\mathcal{O}(n d
m^3)$ where $m$ is the maximum number of underlying basis
functions. This paper uses an implementation of MARS
\shortcite{rudy2017pyearth} with $m = 200$.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,trim={0 .5in 0 .4in}]{Raw_Throughput.pdf}
  \caption{Histograms of 100-bin reductions of the PMF of I/O
    throughput mean (top) and I/O throughput sample variance
    (bottom). In the mean plot, the first 1\% bin (truncated in plot)
    has a probability mass of .45. In the variance plot, the first 1\%
    bin has a probability mass of .58. It can be seen that the
    distributions of throughputs are primarily of lower magnitude with
    occasional extreme outliers.}
  \label{fig:raw_throughput}
\end{figure}

\subsection{Dimensional Analysis}
This work utilizes an extension to standard $k$-fold cross validation
that allows for a more thorough investigation of the expected model
performance in a variety of real-world situations. Alongside
randomized splits, two extra components are considered: the amount of
training data provided, and the dimension of the input data. It is
important to consider that algorithms that perform well with less
training input also require less experimentation. Although, the amount
of training data required may change as a function of the number of
input dimensions and this needs to be studied as well. The framework
used here will be referred to as a multidimensional analysis (MDA) of
the IOzone data.

%% \color{red}

\subsubsection{Multidimensional Analysis}
This procedure combines random selection of training and testing
splits with changes in the input dimension and the ratio of training
size to testing size. Given an input data matrix with $n$ rows
(points) and $d$ columns (components), MDA proceeds as follows:
\begin{enumerate}
\item for all $k = 1, \ldots, d$ and for all subsets of input
  components $F = \{ j_1, j_2, \ldots j_k \}$; reduce the input data
  to unique points $z \in \mathbb{R}^k$ with $f(z) = E[ \{ f(x^{(i)})
    \quad \forall i \quad s.t. \quad (x^{(i)}_F = z) \} ]$ where
  $x^{(i)}_F$ is the $k$-tuple containing only those components of
  $x^{(i)}$ in $F$.
\item for all $r$ in $\{5, 10, \ldots, 95\}$; generate $N$ random
  splits $(train, test)$ of the reduced data with $r$ percentage for
  training and $100 - r$ percentage for testing.
\item when generating each random $(train, test)$ split, ensure that
  all points from $test$ are on or inside the convex hull of points in
  $train$; also ensure that the points in $train$ are well spaced.
\end{enumerate}

In order to ensure that the testing points are inside the convex hull
of training points, this paper identifies the set of (reduced
dimension) points that compose the convex hull and forcibly places
those points in the training set. In order to ensure that training
points are well spaced, this paper relies on the statistical method
for picking points from \shortciteN{amos2014algorithm} that proceeds
as follows:
\begin{enumerate}
\item Generate a sequence of all pairs of points sorted by ascending
  pairwise $L_2$ distance between points, ${(x^{(i_1)},x^{(j_1)}),
    (x^{(i_2)},x^{(j_2)}), \ldots}$ such that
  $||x^{(i_k)}-x^{(j_k)}||_2 \leq ||x^{(i_{k+1})}-x^{(j_{k+1})}||_2$
\item Sequentially remove points from candidacy until only $N$ remain
  by randomly selecting one point from the pair $(x^{(i_k)},
  x^{(j_k)})$ for $k = 1,\ldots$ if both $x^{(i_k)}$ and $x^{(j_k)}$
  are still candidates.
\end{enumerate}

Given the large number of constraints, level of reduction, and use of
randomness in the MDA procedure, occasionally $N$ unique training
testing splits may not be created or may not exist. In these cases, if
there are fewer than $N$ possible splits then deterministically
generated splits are used. Otherwise after $3*N$ attempts, only the
unique splits are kept for analysis. The MDA procedure has been
implemented in python3 while most regression and interpolation methods
are FORTRAN wrapped with python. All randomness has been seeded for
repeatability.

For any input component subset $F$ (of size $k$) and selected value of
$r$, MDA will generate up to $N$ predictions that each multivariate
model has made for each point $z^{(i)} \in \mathbb{R}^k$. There may be
fewer than $N$ predictions made for any given point. Points in the
convex hull for the selected subset of components will always be used
for training, never for testing. Points that do not have any close
neighbors will often be used for training in order to ensure well
spacedness. Finally, as mentioned before, some subsets of components
do not readily generate $N$ unique training and testing splits.

MDA results in a distribution of possible estimates that a given
multivariate model could make for a point in $\mathbb{R}^k$, $k \leq
d$ given component set $F$. The summary results presented in this work
use the expected value of the distributions at each point as the model
estimate for error analysis.

@@

A na\"{\i}ve multivariate prediction technique such as nearest
neighbor could experience relative errors in the range $[0,
  (\text{max}_f - \text{min}_f) / \text{min}_f ]$ when modeling a non
negative function $f$ from data. The IOzone mean data response values
span three orders of magnitude (as can be seen in Table
\ref{tab:data_type}) while variance data response values span six
orders of magnitude. It is expected therefore, that all studied
multivariate models perform better than a na\"{\i}ve approach,
achieving relative errors strictly less than $10^3$ for throughput
mean and $10^6$ for throughput sample variance. Ideally, models will
yield relative errors significantly smaller than 1.

@@

Almost all multivariate models analyzed make predictions with a
relative error less than 1 for most system configurations when
predicting the mean I/O throughput of a system given varying amounts
of training data. The overall best of the multivariate models,
Delaunay, consistently makes predictions with relative error less than
$.05$ (5\% error). In Figure \ref{fig:mean_tt_ratio} it can also be
seen that the Delaunay model consistently makes good predictions even
with as low as 5\% training data (43 of the 864 system configurations)
regardless of the dimension of the data.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,trim={0 .5in 0 .5in}]{Mean_TT_Ratio.pdf}
  \caption{These box plots show the prediction error of mean with
    increasing amounts of training data provided to the models. Notice
    that MARS is the only model whose average spread of performance
    decreases with more training data. Recall that the response values
    being predicted span three orders of magnitude and hence relative
    errors should certainly remain within that range. For SVR the top
    box whisker goes from around 100 to 50 from left to right and is
    truncated in order to maintain focus on more performant models.}
  \label{fig:mean_tt_ratio}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,trim={0 .5in 0 .5in}]{Mean_Dim.pdf}
  \caption{These box plots show the prediction error of mean with
    increasing dimension. The top box whisker for SVR transitions
    \{40, 80, 90\} for dimensions 2, 3, and 4 respectively. Notice
    that each model consistently experiences greater magnitude error
    with increasing dimension.}
  \label{fig:mean_dim}
\end{figure}

@@

The prediction results for variance resemble those for predicting
mean. Delaunay remains the best overall predictor with relative error
of .6 on average and LSHEP closely competes with Delaunay having an
average relative error of -2. Outliers in prediction error are much
larger for all models. Delaunay produces relative errors as large as
78 and other models achieve relative errors around $10^3$. The
relative errors for many models scaled proportional to the increased
orders of magnitude spanned by the variance response compared with
mean response. All models are more sensitive to the amount of training
data provided than their counterparts for predicting mean.

\subsection{Increasing Dimension and Decreasing Training Data}

As can be seen in Figure \ref{fig:mean_dim}, all of the models suffer
increasing error rates in higher dimension. This is expected, because
the number of possible interactions to model grows
exponentially. However, LSHEP and Delaunay maintain the slowest
increase in relative error. The increase in error seen for Delaunay
suggests that it is capable of making predictions with a range of
relative errors that grows approximately linearly with increasing
dimension input. This trend suggests that Delaunay would remain a
viable technique for accurately modeling systems with 10's of
parameters given only small amounts of training data. All models, with
the exception of MARS, produce smaller errors given more training
data. Increasing the amount of training data most notably reduces the
number of prediction error outliers.

@@

The present results demonstrate that a straightforward application of
multivariate modeling techniques can be used to effectively predict
HPC system performance. Little effort on the part of a systems
engineer combined with a minimal amount experimentation can yield a
model capable of accurately tuning an HPC system to the desired
performance specification.

\subsection{Modeling the System}

The modeling techniques generated estimates of drastically different
quality when predicting I/O throughput mean and sample variance. A few
notable characteristics include: the SVR has the largest range of
errors for all selections of dimension and amount of training data;
MARS and LSHEP produce similar magnitude errors while the former
consistently underestimates and the latter consistently overestimates
in predictions; and Delaunay has considerably fewer outliers than all
other methods. SVR likely experiences the greatest quantity of errors
because the underlying parametric representation is global and
oversimplified (a single polynomial), making it unable to capture the
complex local behaviors of system I/O. It is still unclear however
what causes the behaviors of LSHEP, MARS, and Delaunay. An exploration
of this topic is left to future work.

While the Delaunay method appears to be the best predictor in the
presented IOzone case study, it is important to note its significantly
higher computational complexity with respect to the dimension of the
input. The implementation of Delaunay used would experience
unacceptably large training times beyond seven dimensions of
input. This leaves much room for other techniques to perform best in
higher dimension unless a more performant implementation of Delaunay
can be used.

Finally, the ability of the models to predict variance was
significantly worse for I/O sample variance. The larger scale in
variance responses alone do not account for the increase in relative
errors witnessed. This suggests that system variability has an greater
underlying functional complexity when compared with the system mean
and that latent factors are reducing prediction performance
considerably.

\subsection{Extending the Analysis}

System I/O throughput mean and throughput sample variance are simple
and useful system characteristics to model. The process presented in
this work is equally applicable to predicting other useful performance
characteristics of HPC systems such as: computational throughput,
power consumption, processor idle time, context switches, RAM usage,
or any other ordinal performance metric. For each of these there is
the potential to model system variability as well. This work has
chosen variance as a measure of variability, but the techniques used
in this paper could be used to predict more precise measures of
variability such as the percentiles of the performance distribution. A
thorough exploration of HPC systems applications of multivariate
modeling is left to future work.

%% \begin{enumerate}
%% \item Measuring different system characteristics other than I/O
%% \item Recording system performance constantly to maintain model accuracy
%% \end{enumerate}

\section{Conclusion}
\label{sec:conclusion}
Multivariate models of HPC systems produce promising results when
applied to predicting I/O throughput mean and variability. These
multivariate techniques significantly expand the comprehensiveness and
portability of statistical models for predicting computer system
performance over previous works. In the IOzone case study presented,
the Delaunay method produces the best overall results making
predictions for 821 system configurations with less than 5\% error
when trained on only 43 configurations. Analysis also suggests that
the error in the Delaunay method will remain manageable as the number
of system parameters being modeled increases. These multivariate
techniques can and should be applied to HPC systems with more than
four tunable parameters in order to identify optimal system
configurations that may not be discoverable via previous methods nor
by manual performance tuning.

%     Future Work     
%=====================
\subsection{Future Work}
The most severe limitation to the present work is the restriction to
modeling strictly ordinal (not categorical) system parameters. This
could be seen as a limitation of the multivariate models selected,
because only MARS is capable of handling non numeric components, or as
a limitation of the MDA framework. Future work could attempt to
identify the viability of different techniques for making predictions
across varying categorical system paramters.

There remain many other multivariate modeling techniques not included
in this work that should be evaluated and applied to HPC performance
tuning. For I/O alone, there are far more than the four tunable
parameters studied in this work. Alongside experimentation with more
models, there is room for a theoretical characterisation of the
combined model and data properties that allow for the greatest
predictive power.

%% \color{black}

%% \newpage
%% \ \\

@@

%% \texttt{\textbf{L}oc\textbf{A}ll\textbf{Y} li\textbf{NE}ar
%%   \textbf{W}eighted \textbf{A}pproxima\textbf{T}ion\textbf{S}
%%   \textbf{O}f fu\textbf{N}tions}\\
%% %% \texttt{L\ \ A\ \ Y \ \ NE\ \ \  W\ \ \ \ \ \ \ \ A\ \ \ \ \ \ \ \ T\ \ \ S O\ \ \ \ N\ \ \ \ \ \ }
%% \newpage

@@
